\textbf{EECS 340: Assignment 7}

### 2020-04-28 assignment_7/article.tex
🗑️ Remove Yuhui ZHANG's credit as finished individually.

\author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
\date{Due and submitted on 04/27/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
\maketitle

@@

\begin{itemize}
    \item Case 1: $v.d < u.d < u.f < v.f$\newline
    In this case $u$ is a decent of $v$, which means there must be a path of $v \rightarrow u$; and known that we have $uv \in E$ (from the question instruction), this implies there is a direct connection of $u \rightarrow v$. Thus, now we have a path of $v \rightarrow u$ and a path of $u \rightarrow v$, $uv$ is guaranteed to be on a circle.
    \item Case 2: $u.d < u.f < v.d < v.f$\newline
    In this case we have $u$ completely discovered before $v$. This suggest there shoule be no relationship between $u$ and $v$, as $v$ should not be a decendent nor ancestor of $u$. However, it is known from the question that we have $uv \in E$, which implies $v$ must be a decendent of $u$. Thus, this case will not be valid under the question restriction and therefore disregarded.
\end{itemize}

@@

\subsection{Shaochen (Henry) ZHONG's proof of course evalution}

@@

\subsection{Yuhui ZHANG's proof of course evalution}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{{fig/fig_4_b.png}}
\end{figure}

>>>>

\author{Shaochen (Henry) ZHONG, \ilc{sxz517}}
\date{Due and submitted on 04/27/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
\maketitle

@@

\begin{itemize}
    \item Case 1: $v.d < u.d < u.f < v.f$\newline
    In this case $u$ is a decent of $v$, which means there must be a path of $v \rightarrow u$; and known that we have $uv \in E$ (from the question instruction), this implies there is a direct connection of $u \rightarrow v$. Thus, now we have a path of $v \rightarrow u$ and a path of $u \rightarrow v$, $uv$ is guaranteed to be on a circle.
    \item Case 2: $u.d < u.f < v.d < v.f$\newline
    In this case we have $u$ completely discovered before $v$. This suggests there shoule be no relationship between $u$ and $v$, as $v$ should not be a decendent nor ancestor of $u$. However, it is known from the question that we have $uv \in E$, which implies $v$ must be a decendent of $u$. Thus, this case will not be valid under the question restriction and therefore disregarded.
\end{itemize}

@@

@@
